\chapter{Introduction}

\section*{Aim of the project}

\textbf{MangaVerse} is a web application project developed for the Large-scale and 
Multi-structured Databases course at the University of Pisa. 
This web application aims to create a \textbf{comprehensive platform} for 
exploring a vast collection of \textbf{manga} and \textbf{anime}, while also fostering \textbf{interaction} among users.

\vspace{\baselineskip}

The website is accessible without requiring a login, offering a limited set of functionalities. 
However, once users log in, they gain access to a wide range of features designed to \textbf{personalize} 
their experience, particularly through \textbf{social interactions}.

\vspace{\baselineskip}

\textbf{MangaVerse} is designed to be a user-friendly, seamless, and engaging platform for \textbf{manga and anime enthusiasts}, 
to connect with like-minded individuals, discover new content, and share their thoughts and opinions.

\vspace{\baselineskip}

To explore the project development details, here is the URL of the GitHub repository:\\
\url{https://github.com/xDarkFlamesx/MangaUniverse}.

\section*{Application Highlights}

\begin{itemize}
    \item \textbf{Comprehensive Media Database}: MangaVerse offers a vast collection of \textbf{manga} and \textbf{anime} entries,
    complete with detailed information, ratings, and reviews, to help users make informed decisions.

    \item \textbf{Search and Filter Functionality}: Users can easily search for specific \textbf{manga} or \textbf{anime} titles,
    genres, authors, and more, using advanced \textbf{filtering} options to refine their search results.
    
    \item \textbf{User Profiles}: Users can create profiles to \textbf{personalize} their experience, track their activity,
    and connect with other users who share similar interests.

    \item \textbf{User and Media Content Suggestions}: The platform provides tailored suggestions based on user interactions, preferences, 
    and information, enhancing the discovery of new \textbf{manga}, \textbf{anime}, and \textbf{users}.
    
    \item \textbf{Social Features}: Logged-in users can engage with the community through \textbf{reviews}, \textbf{likes}, and \textbf{follows},
    fostering a vibrant community of \textbf{manga} and \textbf{anime enthusiasts}.
    
    \item \textbf{Managerial Roles and Analytics}: MangaVerse includes \textbf{managerial roles} with access to an \textbf{analytics dashboard} 
    for tracking media content and user activities. Managers can \textbf{add, update, or remove} \textbf{manga} and \textbf{anime entries}, monitor trends, 
    and analyze ratings to optimize content offerings.
    
    \item \textbf{Content Management}: Managers can efficiently manage media content and user accounts, 
    ensuring that the platform remains \textbf{up-to-date} and \textbf{relevant}.
\end{itemize}