\chapter{Analisys}

\section{Requirements}
\textbf{Unregistered User}:

\begin{itemize}
    \item Browse Media Contents:
    \begin{itemize}
        \item View a list of available manga and anime on the home page.
        \item Access basic details about each media content without logging in.
    \end{itemize}
    \item Search and Filter:
    \begin{itemize}
        \item Use the search bar to find specific manga or anime by title.
        \item Utilize basic filtering options to refine the media content list.
    \end{itemize}
    \item View Media Content Details:
    \begin{itemize}
        \item Click on a media content to view detailed information, including synopsis and genre.
    \end{itemize}
    \item Register/Login:
    \begin{itemize}
        \item Access a registration page to create a new account.
        \item Use valid credentials to log into the account.
    \end{itemize}
    \item Explore Features:
    \begin{itemize}
        \item Access information about the features available to registered users.
    \end{itemize}
\end{itemize}

\textbf{Registered User}:

\begin{itemize}
    \item Browse Media Contents:
    \begin{itemize}
        \item View a list of available manga and anime on the home page.
        \item Access basic details about each media content without logging in.
    \end{itemize}
    \item Search and Filter:
    \begin{itemize}
        \item Use the search bar to find specific media content by title.
        \item Utilize basic filtering options to refine the media content list.
    \end{itemize}
    \item View Media Content Details:
    \begin{itemize}
        \item Click on a media content to view detailed information, including synopsis and genre.
    \end{itemize}
    \item Logout:
    \begin{itemize}
        \item Ends the user's session.
    \end{itemize}
    \item Profile Management:
    \begin{itemize}
        \item Edit and update personal information (e.g., profile picture, bio).
        \item Change account password.
    \end{itemize}
    \item Explore Other User Profiles:
    \begin{itemize}
        \item View profiles of other registered users.
        \item See their liked manga, anime and reviews.
    \end{itemize}
    \item Interact with Media Contents/Users:
    \begin{itemize}
        \item Like or dislike manga and anime to indicate preferences.
        \item Follow/unfollow other users.
    \end{itemize}
    \item Review Media Contents:
    \begin{itemize}
        \item Add reviews and ratings to manga and anime.
        \item View and edit own reviews.
    \end{itemize}
    \item Advanced Recommendations:
    \begin{itemize}
        \item Receive more refined media content suggestions based on detailed user interactions.
        \item Receive users suggestions based on common interests.
    \end{itemize}
\end{itemize}

\textbf{Manager}(Registered User with Administrative Features):

\begin{itemize}
    \item Analytics Dashboard:
    \begin{itemize}
        \item Access a comprehensive analytics dashboard with data on user engagement and media contents trends.
    \end{itemize}
    \item User Management:
    \begin{itemize}
        \item View and manage user accounts, including account activation and deactivation.
    \end{itemize}
    \item Content Management:
    \begin{itemize}
        \item Manage media content entries, including adding new manga and anime, updating information, and removing entries if necessary.
    \end{itemize}
    \item Monitor Trends:
    \begin{itemize}
        \item Monitor trends in user interactions, popular genres, and trending manga.
    \end{itemize}
\end{itemize}

\section{Non Functional Requirements}

\textbf{Performance}

\begin{itemize}
    \item Response Time: The system should have low latency, with pages loading within an acceptable timeframe.
    \item Scalability: The system should be able to handle an increasing number of users and data without significant degradation in performance.
    \item Concurrency: The application should support multiple users simultaneously without performance bottlenecks. For very high traffic scenarios, acceptable delays may be introduced.
\end{itemize}

\textbf{Security}

\begin{itemize}
    \item Data Encryption: All user data, including passwords, should be securely encrypted during transmission and storage.
\end{itemize}

\textbf{User Interface}

\begin{itemize}
    \item Responsiveness: The user interface should be responsive, providing a consistent and seamless experience across various devices and screen sizes.
    \item Intuitiveness: The interface should be user-friendly, with clear navigation and easily understandable features.
\end{itemize}
